Sterile Neutrinos, a Summary

### 2015-04-14 p3_505/presentation/pres.tex
first (combining all the old repos and adding project 3)
skeletoning
presentation blah
figures stuff and a little presentation
miniboone slide done

\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath}
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\pgfdeclareimage[height=1.7cm]{atlaslogo}{logos/atlas_logo.pdf}
\pgfdeclareimage[height=1.7cm]{dukelogo}{logos/dukelogo.pdf}
\title[PHY 505 Project 2]{Mesons Beyond \su3flavor \qqbar}
\author[DD, ME, JR, PZ]{{\small Douglas Davis, Matthew Epland, Justin Raybern, Pingchuan Zhao}}
\institute{\it{Duke University} \\ \mbox{} \\ \mbox{} \\ \pgfuseimage{dukelogo}}
\date[19 March 2014]{19 March 2014}

\DeclareRobustCommand{\su3flavor}{$\text{SU(3)}_{\text{flavor}}$}
\DeclareRobustCommand{\qqbar}{$q\overline{q}$}

@@

\begin{frame}
  \frametitle{Outline}
  \begin{itemize}
  \item Introduction to non \su3flavor mesons.
  \item Theoretical states:
    \begin{itemize}
    \item QCD Hybrids
    \item Glueballs
    \item Tetraquarks
    \end{itemize}
  \item Discussion of the $\pi_1(1400)$ and $\pi_1(1600)$ exotics.
  \item Discussion of the $Z(4430)$ tetraquark.
  \item Summary
  \end{itemize}
\end{frame}

@@

\begin{thebibliography}{9}
  %\bibitem{Barnes}
  %  T. Barnes, \textit{Exotic Mesons, Theory and Experiment}, arXiv:hep-ph/0007296, \url{http://arxiv.org/abs/hep-ph/0007296}
\bibitem{ketzer}
  Bernhard Ketzer, \textit{Hybrid Mesons}, Proceedings of Science, Sixth International Conference on Quarks and Nuclear Physics, PoS(QNP2012)025, \url{http://pos.sissa.it/archive/conferences/157/025/QNP2012_025.pdf} %\url{http://arxiv.org/abs/1208.5125}
  %\bibitem{Olsen}
  %  Stephen Lars Olsen, \textit{QCD exotics}, Hyperfine Interactions, \textbf{229}, \url{http://dx.doi.org/10.1007/s10751-014-1061-4}
\bibitem{belle}
  S.~K.~Choi~\emph{et. al.}, \emph{Observation of a Resonancelike Structure in the} $\pi^{+-}\psi^{\prime}$ \emph{Mass Distribution in Exclusive} $B\rightarrow K \pi^{+-}\psi^{\prime}$ \emph{Decays}. Phys. Rev. Lett. \textbf{100}, 142001 8 April 2008.
\bibitem{z4430_dmolecule}
  E.~Braaten~and~M.~Lu, \emph{Line shapes of the Z(4430)} Phys. Rev. D \textbf{79} 051503(R) 11 March 2009
\bibitem{lhcb} % {j4}
  LHCb Collaboration, R. Aaij \textit{et al.}, \textit{Observation of the Resonant Character of the }$Z(4430{)}^{-}$\textit{ State}, Phys. Rev. Lett., \textbf{112}, 22 (2014). \url{http://dx.doi.org/10.1103/PhysRevLett.112.222002}%\url{http://link.aps.org/doi/10.1103/PhysRevLett.112.222002}

>>>>

\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath}
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\pgfdeclareimage[height=1.7cm]{atlaslogo}{logos/atlas_logo.pdf}
\pgfdeclareimage[height=1.7cm]{dukelogo}{logos/dukelogo.pdf}
\title[PHY 505 Project 3]{Sterile Neutrinos, a Summary}
\author[DD, ME, JR, PZ]{{\small Douglas Davis, Matthew Epland, Justin Raybern, Pingchuan Zhao}}
\institute{\it{Duke University} \\ \mbox{} \\ \mbox{} \\ \pgfuseimage{dukelogo}}
\date[15 April 2014]{15 April 2014}

@@

\begin{frame}
  \frametitle{Outline}
  \begin{itemize}
  \item neutrinos are kewl
  \item and maybe sterile who knows
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{The LSND Experiment}
  \footnotesize{
    \begin{columns}
      \begin{column}{.5\linewidth}      
        \begin{itemize}
        \item Liquid Scintillator Neutrino Detector.
        \item Los Alamos National Laboratory from 1993 to 1998.
        \item Cherenkov detector using 1220 PMTs.
        \item Protons strike target, use pions decaying at test to product $\overline{\nu}_\mu$.
        \end{itemize}
      \end{column}
      \begin{column}{.5\linewidth}
        \begin{itemize}
        \item $117.9 \pm 22.4$ events, signal excess of $87.9\pm 22.4 \pm 6.0$.
        \item $(\sin^2 2\theta,\Delta m^2)$ fit extracts allowed oscillation regions.
        \item Best fits yields $\Delta m^2 \sim 1$ eV.
        \item Disagrees with solar and atmospheric oscillation experiments and also LEP experiments for 3 light flavor neutrinos.
        \end{itemize}
      \end{column}
    \end{columns}
  }
  \begin{center}
    \includegraphics[width=.35\linewidth]{../figures/LSND_plot.pdf}
  \end{center}
\end{frame}
\begin{frame}
  \frametitle{The MiniBooNE Experiment}
  \scriptsize{
    \begin{columns}
      \begin{column}{.5\linewidth}      
        \begin{itemize}
        \item Developed to answer the LSND anomaly.
        \item Collected data at Fermilab from 2002 to 2012
        \item Cherenkov detector using PMTs (just like LSND)
        \item 8 GeV protons from the Booster strike beryllium target, pions decay producing neutrinos
        \begin{center}
          \includegraphics[width=.9\linewidth]{../figures/miniboone_excess.pdf}
        \end{center}
        \end{itemize}
      \end{column}
      \begin{column}{.5\linewidth}
        \begin{itemize}
        \item Consistent with the LSND anti neutrino oscillation result.
          \begin{center}
            \includegraphics[width=.6\linewidth]{../figures/miniboone_regions.pdf}
          \end{center}
        \item Detector systematics make it difficult to differentiate between $\pi^0\rightarrow\gamma\gamma$ and an electron in the detector.
        \end{itemize}
      \end{column}
    \end{columns}
  }
\end{frame}

\end{document}

%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%

% \DeclareRobustCommand{\su3flavor}{$\text{SU(3)}_{\text{flavor}}$}
% \DeclareRobustCommand{\qqbar}{$q\overline{q}$}

@@

\begin{thebibliography}{9}
  % \bibitem{Barnes}
  %   T. Barnes, \textit{Exotic Mesons, Theory and Experiment}, arXiv:hep-ph/0007296, \url{http://arxiv.org/abs/hep-ph/0007296}
\bibitem{ketzer}
  Bernhard Ketzer, \textit{Hybrid Mesons}, Proceedings of Science, Sixth International Conference on Quarks and Nuclear Physics, PoS(QNP2012)025, \url{http://pos.sissa.it/archive/conferences/157/025/QNP2012_025.pdf} %\url{http://arxiv.org/abs/1208.5125}
  % \bibitem{Olsen}
  %   Stephen Lars Olsen, \textit{QCD exotics}, Hyperfine Interactions, \textbf{229}, \url{http://dx.doi.org/10.1007/s10751-014-1061-4}
\bibitem{belle}
  S.~K.~Choi~\emph{et. al.}, \emph{Observation of a Resonancelike Structure in the} $\pi^{+-}\psi^{\prime}$ \emph{Mass Distribution in Exclusive} $B\rightarrow K \pi^{+-}\psi^{\prime}$ \emph{Decays}. Phys. Rev. Lett. \textbf{100}, 142001 8 April 2008.
\bibitem{z4430_dmolecule}
  E.~Braaten~and~M.~Lu, \emph{Line shapes of the Z(4430)} Phys. Rev. D \textbf{79} 051503(R) 11 March 2009
\bibitem{lhcb} % {j4}
  LHCb Collaboration, R. Aaij \textit{et al.}, \textit{Observation of the Resonant Character of the }$Z(4430{)}^{-}$\textit{ State}, Phys. Rev. Lett., \textbf{112}, 22 (2014). \url{http://dx.doi.org/10.1103/PhysRevLett.112.222002}%\url{http://link.aps.org/doi/10.1103/PhysRevLett.112.222002}
